Presentation Title

### 2017-08-05 thesis/chapters/ch1-intro.tex
Write preface and update Bitcoin situation

Bitcoin has had its ups and downs, but over it has grown into an enormous system.
Its power consumption is as high as Republic of Ireland~\cite{o2014bitcoin}.
Its market cap, at the time of writing, is over 40 billion USD~\cite{bitcoinmarketcap}.
% TODO add graph
Many online marketplaces are using Bitcoin, for example Steam\footnote{\url{https://store.steampowered.com/}} and even Amazon\footnote{Not directly, but via \url{https://purse.io/}.}.
Due to its success, people from many different disciplines began investigating in way to use blockchain technology.
This includes finance~\cite{finance}, heathcare~\cite{healthcare}, logistics~\cite{supplychain} and energy~\cite{energy}.

Sadly, as traditional blockchain systems began to gain popularity,
their limitations also became apparent.
Bitcoin has the infamous 7 transactions per second upper bound~\cite{vukolic2015quest}.
This is due to the fact that blocks are fixed to 1 MB are only generated on average every 10 minutes.
Since every Bitcoin transaction is at least 250 bytes, it computes to about 7 transactions per second.
Due to this limitation, it is not uncommon to see a long backlog of about 20,000 transactions\footnote{\url{https://blockchain.info/unconfirmed-transactions/}}.
A few months ago the backlog even reached 100,000, which meant new transactions would take at least 11 hours to be written to the blockchain~\cite{bitcoinbacklog}.
% TODO update below
This issue has plagued the Bitcoin community for some time and is the root cause for the block size debate, which some calls it a civil war~\cite{bitcoincivilwar}.
Parties that are for the increase in block size argue that a larger block would improve the transaction rate.
Parties against it argue that it would make mining more centralised because blocks take longer to propogate through the network.
It also requires a hard fork (not backward compatible), which risks consensus failure and devaluation.
% TODO update the above
A recent empirical study by Croman et el.~\cite{croman2016scaling} has shown that increasing the block size may help.
But given the bandwidth and latency constraints,
it is not possible to have more than 758 transactions per second.
Even worse, it may give some miner an unfair lead over others.
Thus fundamental changes are necessary run at the scale of centralised payment processors such as Visa,
which is in the order of tens of thousands transactions per second~\cite{visa}.

% TODO update
What we have described is in fact the current state of Bitcoin.
Many proposals exist with the aim to make Bitcoin more scalable.
The most prominant is Seggregated Witness or SegWit~\cite{segwit}.
It moves the signature data to the end of the block and changes the block size to 4 MB.
The effect is that the first 1 MB of the block is still backward compatible, thus there is no need for a hard fork.
It also solves the transaction malleability problem~\cite{bitcoinmalleability} and paves the way for offchain transactions via Lightning Network~\cite{lightningnetwork}.
Although SegWit is implemented, it is still uncertain whether the Bitcoin network will adopt it.
At the time of writing, there is only 35\% of the network signalling for adoptation,
this is only a 10\% increase since November last year\footnote{\url{https://blockchain.info/charts/bip-9-segwit}}.
Thus it may take years if ever for SegWit to be adopted.
Even if it is adopted, it cannot reach the transaction rate of centralised systems.
% https://www.bloomberg.com/news/articles/2017-07-10/bitcoin-risks-splintering-as-civil-war-enters-critical-month

@@

Using the aforementioned insight,
we explore an alternative consensus model for blockchain systems where transactions themself do not reach consensus,
but nevertheless verifiable at a later stage by any node in the network.
Informally, our system works as follows.
Every node stores its own blockchain and every block is one transaction.
We randomly select nodes in every round, the selected ones are called facilitators.
They reach consensus not on the individual transactions,
but on the state of every chain represented by a single digest, we call this state the checkpoint.
If a checkpoint of some node is in consensus, 
then that node can proof to any other node that it holds a set of transactions that computes (form a chain) to the checkpoint.
This immediately show that those transactions are tamper-proof.
We call our protocol CheckpointConsensys.
% TODO mention consensus and trade off?

Our main contributions are the following.
\begin{itemize}
    \item We formally introduce a blockchain system---CheckpointConsensys.
        It uses individual hash chains and checkpoints on every node to achieve
        horizontally scalable for the first time.
    \item We formally analyse CheckpointConsensys to ensure correctness as defined in our architecture.
    \item We implement Checkpiont Consensus with experiment with up to 1200 nodes,
        our results show strong evidence of horizontal scalability.
\end{itemize}

>>>>

Bitcoin has had its ups and downs, but over it has grown into an enormous system.
Its power consumption is as high as Republic of Ireland~\cite{o2014bitcoin}.
Its market capitalisation, at the time of writing, is over 60 billion USD~\cite{bitcoinmarketcap} and growing (\Cref{fig:market-cap}).
\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{market-cap}
\caption{Market capitalisation and price of Bitcoin, graph is extracted from~\cite{bitcoinmarketcap}.}
\label{fig:market-cap}
\end{figure}
Many online marketplaces are using Bitcoin, for example Steam\footnote{\url{https://store.steampowered.com/}} and even Amazon\footnote{Not directly, but via \url{https://purse.io/}.}.
Due to its success, people from many different disciplines began investigating in way to use blockchain technology.
This includes finance~\cite{finance}, heathcare~\cite{healthcare}, logistics~\cite{supplychain} and energy~\cite{energy}.

Sadly, as traditional blockchain systems began to gain popularity,
their limitations also became apparent.
Bitcoin has the infamous 7 transactions per second upper bound~\cite{vukolic2015quest}.
This is due to the fact that blocks are fixed to 1 MB are only generated on average every 10 minutes.
Since every Bitcoin transaction is at least 250 bytes, it computes to about 7 transactions per second.
Due to this limitation, it is not uncommon to see a long backlog of about 20,000 transactions\footnote{\url{https://blockchain.info/unconfirmed-transactions/}}.
A few months ago the backlog even reached 100,000, which meant new transactions would take at least 11 hours to be written to the blockchain~\cite{bitcoinbacklog}.
This issue has plagued the Bitcoin community for some time and is the root cause for the block size debate, which some calls it a civil war~\cite{bitcoincivilwar}.
Parties that are for the increase in block size argue that a larger block would improve the transaction rate.
Parties against it argue that it would make mining more centralised because blocks take longer to propogate through the network.
It also requires a hard fork (not backward compatible), which risks consensus failure and devaluation.
A recent empirical study by Croman et el.~\cite{croman2016scaling} has shown that increasing the block size may help.
But given the bandwidth and latency constraints,
it is not possible to have more than 758 transactions per second.
Even worse, it may give some miner an unfair lead over others.
Thus fundamental changes are necessary run at the scale of centralised payment processors such as Visa,
which is in the order of tens of thousands transactions per second~\cite{visa}.

What we have described is in fact the current state of Bitcoin.
Many proposals exist with the aim to make Bitcoin more scalable.
The most prominant is Seggregated Witness or SegWit~\cite{segwit}.
It moves the signature data to the end of the block and uses a variable block size up to 4 MB.
The effect is that the first 1 MB of the block is still backward compatible, thus there is no need for a hard fork.
It also solves the transaction malleability problem~\cite{bitcoinmalleability} and paves the way for offchain transactions via Lightning Network~\cite{lightningnetwork}.
However, some fear SegWit is not enough and wish to see a hard fork that uses ``Adjustable Blocksize Cap'' that increase the block size up to 8 MB\footnote{\url{https://www.bitcoinabc.org/}}.
The ongoing civil war resulted in a Bitcoin fork, called Bitcoin Cash\footnote{\url{https://www.bitcoincash.org/}}.
At the time of writing, it is too early to speculate how these proposals and forks may affect the scalability properties of Bitcoin.
But the conclusion that we can draw from the scalability debate is that the Bitcoin design is fundamentally not scalable,
and it is highly non-trivial to ``patch'' the problem.

@@

Using the aforementioned insight,
we explore an alternative consensus model for blockchain systems where transactions themself do not reach consensus,
but nevertheless verifiable at a later stage by any node in the network.
Informally, our system works as follows.
Every node stores its own blockchain and every block is one transaction.
We randomly select nodes in every round, the selected ones are called facilitators.
They reach consensus not on the individual transactions,
but on the state of every chain represented by a single digest, we call this state the checkpoint.
If a checkpoint of some node is in consensus, 
then that node can proof to any other node that it holds a set of transactions that computes (form a chain) to the checkpoint.
This immediately show that those transactions are tamper-proof.
We call our protocol Checo, derived from \emph{che}ckpoint \emph{co}nsensus.
% TODO mention consensus and trade off?

Our main contributions are the following.
\begin{itemize}
    \item We formally introduce a blockchain system---Checo.
        It uses individual hash chains and checkpoints on every node to achieve
        horizontally scalable for the first time.
    \item We formally analyse Checo to ensure correctness as defined in our architecture.
    \item We implement Checkpiont Consensus with experiment with up to 1200 nodes,
        our results show strong evidence of horizontal scalability.
\end{itemize}

### 2017-08-05 thesis/formalities/preface.tex
Write abstract
Write preface and update Bitcoin situation

\chapter*{Preface}
\addcontentsline{toc}{chapter}{Preface}
TODO MOTIVATION FOR RESEARCH TOPIC

@@

\noindent
TODO ACKNOWLEDGEMENTS

@@

\noindent
TODO AUTHOR

>>>>

\chapter*{Preface}
\addcontentsline{toc}{chapter}{Preface}
I mined my first Bitcoin in early 2013 with a GPU.
Since then, I have been interested in decentralising the tradationally centralised systems.
Following the Snowden revelations, the interest became a burning desire.
Today, many blockchain systems are mature, but still not yet ready for ubiquitous use due to the scalability limitation.
Many of us still do not use Bitcoin to purchase everyday goods, online or offline.
This limitation as well as my personal ambitions led me to this thesis,
with the goal of creating a truely horizontally scalable solution.

@@

\noindent
There are a number of people who have supported me in this endeavour who I would like to thank.
My supervisor Dr. Johan Pouwelse, your unrivaled enthusiasm and guidance have kept me motivated and productive.
Dr. Zhijie Ren, this work would not have been possible without your invalueable input and the numerous discussions which we have had.
Members of the Tribler team---Martijn de Vos, Quinten Stokkink and Chengxin Ma,
you have my gratitude for helping me with the implementation and proofreading my work.
Members of the Cybersecurity group---Dr. Zekeriya Erkin and O\u{g}uzhan Ersoy,
I thank both of your for your feedback on my presentations.

@@

\noindent
Kelong Cong
